Information Closure Theory of Consciousness

### 2020-04-03 ICT_Frontiers_rev202001.tex
Local update

            \subsubsection*{Informational is not Closed}\label{sec:reflexive}
                If a process is not informationally closed, the degree of NTIC is low (Eq.~\ref{eq:nticObjective2}) resulting in low or no consciousness. In such cases, the current state of a process depends primarily on the environment state (see Fig.~\ref{fig:reflexive}), but receives little influence from its past state. Reflexive behaviours \citep{casali2013theoretically} can be considered an example of this scenario. In \ac{OurTheory}, if we can view reflexive behaviours as situations in which the internal state $Y_t$, which triggers reflexive action, is determined by the environment state $E_{t-1}$ overruling the influences from its own past $Y_{t-1}$.  Such interpretation of reflexive behaviour from the viewpoint of \ac{OurTheory} naturally explains why reflexes do not involve conscious experience of external stimuli.

>>>>

            \subsubsection*{Processes are not Informationally Closed}\label{sec:reflexive}
           		If the environment is info closed we could copy it to get closure. In realistic situations we are not sure whether the environment is informationally closed but even if we assume it is we can confidently assert that we don't observe it completely and that the part we do observe (our sensory values) are not themselves closed. For example, the images on our retina are insufficient to predict their successors without imagining the outside world behind them. This imagining however requires internal processing like recurrent connections.

                If a process is not informationally closed, the degree of NTIC is low (Eq.~\ref{eq:nticObjective2}) resulting in low or no consciousness. In such cases, the current state of a process depends primarily on the environment state (see Fig.~\ref{fig:reflexive}), but receives little influence from its past state. Reflexive behaviours \citep{casali2013theoretically} can be considered an example of this scenario. In \ac{OurTheory}, if we can view reflexive behaviours as situations in which the internal state $Y_t$, which triggers reflexive action, is determined by the environment state $E_{t-1}$ overruling the influences from its own past $Y_{t-1}$.  Such interpretation of reflexive behaviour from the viewpoint of \ac{OurTheory} naturally explains why reflexes do not involve conscious experience of external stimuli.
